SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-15 scipy-1.0/paper.tex
Replace Numeric manual URL with new numpy.org hosted one

With a rich programming environment and a numerical array object in
place, the time was ripe for the development of a full scientific
software stack.  Many of the first efforts were driven by graduate
students and post-doctoral researchers, but soon attracted the
attention of senior researchers.
% Paul Dubois, CDAT
% https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html
Paul Dubois at Lawrence Livermore National Laboratories took over the
maintenance of Numeric and funded the writing of its
manual\footnote{http://people.csail.mit.edu/jrennie/python/numeric/numeric-manual.pdf}.
\fixme{replace this URL with numpy.org hosted version }% Make sure we host this PDF somewhere in the numpy GitHub org
%in the Program for Climate Model Diagnosis and Intercomparison at
%Lawrence Livermore National Laboratory built their Climate Data
%Analysis Tools (``an open-source set of Python modules and tools for
%accessing, manipulating, and plotting scientific data in general and
%climate data sets in
%particular''\footnote{https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html})
%on Numeric, the newly established Python array object.  Paul later
%became the maintainer for Numeric, and helped fund the writing of the
%first manual\footnote{https://conference.scipy.org/scipy2010/slides/travis_oliphant_keynote.pdf}
In 1998, the Space Telescope Science Institute, in charge of science
operations of the Hubble Space Telescope, decided to replace their
custom scripting language with Python\footnote{https://conference.scipy.org/scipy2011/slides/greenfield\_keynote\_astronomy.pdf}.

>>>>

With a rich programming environment and a numerical array object in
place, the time was ripe for the development of a full scientific
software stack.  Many of the first efforts were driven by graduate
students and post-doctoral researchers, but soon attracted the
attention of senior researchers.
% Paul Dubois, CDAT
% https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html
Paul Dubois at Lawrence Livermore National Laboratories took over the
maintenance of Numeric and funded the writing of its
manual\footnote{http://www.numpy.org/\_downloads/numeric-manual.pdf}.
%in the Program for Climate Model Diagnosis and Intercomparison at
%Lawrence Livermore National Laboratory built their Climate Data
%Analysis Tools (``an open-source set of Python modules and tools for
%accessing, manipulating, and plotting scientific data in general and
%climate data sets in
%particular''\footnote{https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html})
%on Numeric, the newly established Python array object.  Paul later
%became the maintainer for Numeric, and helped fund the writing of the
%first manual\footnote{https://conference.scipy.org/scipy2010/slides/travis_oliphant_keynote.pdf}
In 1998, the Space Telescope Science Institute, in charge of science
operations of the Hubble Space Telescope, decided to replace their
custom scripting language with Python\footnote{https://conference.scipy.org/scipy2011/slides/greenfield\_keynote\_astronomy.pdf}.
